\normalfont\spacedallcaps{The economic consequences of different attitudes of a policy maker: a combined epidemiological-econometric study}

### 2021-03-14 Manuscript/manuscript.tex
PUB

\section{Supporting information A}

@@

\section{Supporting information B}

@@

\begin{table}
\centering
\caption{Clothing}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.33  & 0.08  \\ \hline
$\Delta_{T1}$   & -36.33 & 2.15  \\ \hline
$\Delta_{T2}$   & -56.23 & 2.77   \\ \hline
$\Delta_{T3}$   & -11.95 & 2.86 \\ \hline
\label{ASS_Clothing}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Footwear}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
$\Delta_{T1}$   & -38.70 & 1.91   \\ \hline
$\Delta_{T2}$   & -63.21 & 2.47  \\ \hline
$\Delta_{T3}$   & -17.61 & 2.54  \\ \hline
\label{ASS_Footwear}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Appliances}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
$\Delta_{T1}$   & -19.21 & 3.10   \\ \hline
$\Delta_{T2}$   & -26.23 & 4.00  \\ \hline
$\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
\label{ASS_Appliances}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Photo-optics}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.40  & 0.07 \\ \hline
$\Delta_{T1}$   & -29.94 & 2.73   \\ \hline
$\Delta_{T2}$   & -48.11 & 3.52  \\ \hline
$\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
\label{ASS_Photooptics}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household kids}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.16  & 0.04  \\ \hline
$\Delta_{T1}$   & -10.51 & 1.55  \\ \hline
$\Delta_{T2}$   & -19.00 & 2.14  \\ \hline
$\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
\label{ASS_Household_K}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household tools}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.21 & 0.05  \\ \hline
$\Delta_{T1}$   & -13.02 & 3.53 \\ \hline
$\Delta_{T2}$   & -30.23 & 4.88  \\ \hline
$\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
\label{ASS_Household_T}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Games}
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\Delta$ Slope before T1 & -0.37 & 0.10 \\ \hline
$\Delta_{T1}$   & -27.56 & 3.63 \\ \hline
$\Delta_{T2}$   & -64.31 & 5.01  \\ \hline
$\Delta_{T3}$   & 0.27 & 5.01\\ \hline
\label{ASS_Games}
\end{tabular}
\end{table}

@@

\section{Supporting information C}

@@

>>>>

\section{Supporting information}

\subsection{A}

@@

\subsection{B}

@@

\begin{table}
\centering
\caption{Clothing}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.33  & 0.08  \\ \hline
$\Delta_{T1}$   & -36.33 & 2.15  \\ \hline
$\Delta_{T2}$   & -56.23 & 2.77   \\ \hline
$\Delta_{T3}$   & -11.95 & 2.86 \\ \hline
\label{ASS_Clothing}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Footwear}
\begin{tabular}{l|l|l}
                & Value  &  $\sigma$ \ \\ \hline
$\Delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
$\Delta_{T1}$   & -38.70 & 1.91   \\ \hline
$\Delta_{T2}$   & -63.21 & 2.47  \\ \hline
$\Delta_{T3}$   & -17.61 & 2.54  \\ \hline
\label{ASS_Footwear}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Appliances}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
$\Delta_{T1}$   & -19.21 & 3.10   \\ \hline
$\Delta_{T2}$   & -26.23 & 4.00  \\ \hline
$\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
\label{ASS_Appliances}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Photo-optics}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.40  & 0.07 \\ \hline
$\Delta_{T1}$   & -29.94 & 2.73   \\ \hline
$\Delta_{T2}$   & -48.11 & 3.52  \\ \hline
$\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
\label{ASS_Photooptics}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household kids}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.16  & 0.04  \\ \hline
$\Delta_{T1}$   & -10.51 & 1.55  \\ \hline
$\Delta_{T2}$   & -19.00 & 2.14  \\ \hline
$\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
\label{ASS_Household_K}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Household tools}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.21 & 0.05  \\ \hline
$\Delta_{T1}$   & -13.02 & 3.53 \\ \hline
$\Delta_{T2}$   & -30.23 & 4.88  \\ \hline
$\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
\label{ASS_Household_T}
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Games}
\begin{tabular}{l|l|l}
                & Value  & $\sigma$ \\ \hline
$\Delta$ Slope before T1 & -0.37 & 0.10 \\ \hline
$\Delta_{T1}$   & -27.56 & 3.63 \\ \hline
$\Delta_{T2}$   & -64.31 & 5.01  \\ \hline
$\Delta_{T3}$   & 0.27 & 5.01\\ \hline
\label{ASS_Games}
\end{tabular}
\end{table}

@@

\subsection{C}

@@

\subsection{D}

Here we report the estimation of the other parameters, obtained in the DID regression,  that were not put in to the main text

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
& $\alpha $&   $ \sigma_{\alpha}$   & t      & $C$ & $\sigma_{C}$ & t      &  $\beta_{1}$ & $\sigma_{\delta_{1}$  & t     \\ \hline
{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 & 1.47 & 1.69 & 0.87 \\ \hline
{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27 & 1.47  & 2.44  & 0.60  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00 & 1.47  & 2.49  & 0.59 \\ \hline
{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08    & 1.47   & 3.43 & 0.43  \\ \hline
{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 &  1.47 &  3.39 & 0.43
\end{tabular}
\label{selling_DID_table_par_1}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}[]
\caption{
\begin{flushleft}
$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
\end{flushleft}
}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
& $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 \\ \hline
{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 \\ \hline
{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27  \\ \hline
{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00  \\ \hline
{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33    \\ \hline
{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08   \\ \hline
{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 
\end{tabular}
\label{selling_DID_table_par_1}
\end{table}
\end{landscape}
